A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-19 sanity/paper1.tex
Put bibtex back in
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1102 43ef1190-90fd-4dd7-a769-d0121f02b80e
Helen proofreading
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1103 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web.

@@

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. 
The objectives of this paper are:
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}
The contributions of this paper are to meet these objective by means
of a survey that shows that while the uptake has been moderate,
practical benefits may be realized already. Based on this survey as
well as practical experience, we point out future research directions
as well as some recommendations for deployed implementations.

@@

Caching may be deployed at several different levels: An HTTP cache may
be in a reverse proxy close to the server, in which case it may have
much in common with a conventional database cache. It may also be
anywhere between a server and a client, in which case it may be
shared, i.e. it may cache responses from several servers served to
several clients. Another example is an institutional forward proxy,
which are close to several users. Finally, the User Agent may
implement a private cache for its user at the client side.

@@

As mentioned, the two documents from the HTTP 1.1 standards suite that
are relevant for this study are RFC7234, which is named ``Caching''
and RFC7232, named ``Conditional Requests''. The main difference is
that the caching standard defines when a response may be reused
without contacting the origin server at all, whereas the conditional
requests define how to validate a response by contacting the origin
server. The two can be combined: Clients and proxies may use the
latter to revalidate a response that has been cached based on the
former.

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. It can also
be based on heuristics, and Section~4.2.2 in RFC7234 provides some loose
constraints for such practice, as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach therefore still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients that have obtained these values
may use them to validate an earlier response by using
\httph{If-None-Match} and/or \httph{If-Modified-Since} respectively in
a subsequent request. If the server finds the response has not changed
based on this, it will respond with a \httph{304} status code and no
body, otherwise it will return the full response. The other headers we
recorded are listed in Table~\ref{tab:headers}.

@@

We are not aware of any surveys of this type. Although the database
literature is rich with query cache literature, it is mostly relevant
to what would happen within the server or between the server and a
reverse proxy, which is opaque to the Internet, and therefore not of
our concern. For the same reason, caching that happens within the
SPARQL engine is not our concern.

@@

Linked Data Fragments is claimed in \cite{ldf1} to take advantage of
caching and contrasts this with the unavailability of SPARQL query
caches, and it is claimed that this is an architectural problem. In
\cite{hogan2014paths}, the authors examine cacheable as one of the
desiderata for sustainable data access. They claim, without further
justification, that SPARQL isn't cacheable.

@@

In \cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.

In the broader Web literature, \cite{ager2010revisiting} analysed the
value of caching based anonymized traces of actual Web usage at a
major Internet Service Provider. They find that while caching often
yields little benefit when content is user-generated, they still find
some potential.

@@

\section{Methodology}
We want to find information resources on the Web, and examine HTTP
headers that may allow caching. To do this, we perform GET requests on
SPARQL endpoints, vocabularies, dataset descriptions and other
resources and record headers recommended by current standards, as well
as obsoleted and non-standard headers. Additionally, we examine the
triples in the returned information resources to see if there is
information there that may be used to calculate heuristic freshness.

We make several approaches to ensure that we visit a large and
representative section of the open Semantic Web. We take SPARQL
Endpoints from the SPARQLES survey \cite{buil2013sparql}, vocabularies
from Linked Open Vocabularies (LOV) \cite{lov2} and prefix.cc, and we
augment these data with spidered data from the Billion Triple
Challenge (BTC) 2014 \cite{btc-2014} dataset. Of these, BTC2014 is by
far the largest, the others are small, curated and targeted
datasets. However, the size is besides the point, we are only
interested in examining as many hosts as possible, and they are still
few.

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN), as well as other sources. To compile a list of
candidates to further examine, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process is given in a companion technical report
\cite{kjernsmo_add_survey_2015}.

@@

Key challenges to the validity of the survey are biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represent the breadth of the Semantic Web, momentarily at least.

@@

First, we investigated whether certain server implementations provided
better support for caching than others. To do this, we formulated
SPARQL queries to examine the \httph{Server} headers of successful
responses, with optional clauses matching the standards-compliant
computed freshness lifetime (which is the ideal) as well as whether
the response had other indications of caching-related metadata that
may assist caching such as modification time, certain predicates, etc.

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which are partly
developed by and runs on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in the companion technical report
\cite{kjernsmo_add_survey_2015}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints. DBPedia has historically been updated
only a few times a year, but this was probably chosen so as to not
make a commitment long into the future. It may provide considerable benefits.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001 (note, however, it is more contrived
than above, since the bins are like in Figure~\ref{fig:hardtable},
which is chosen for intuitive interpretation rather than statistical
rigor). Second, we note that it is often prohibited to cache dataset
descriptions. This is odd, since statistics about datasets is usually
costly to compute and should be cached. The VoID specification
\cite{voidnote} also notes that the statistics are considered
estimates.

@@

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In
Figure~\ref{fig:heuristicall}, we see that the distribution of
lifetimes are radically different from the case in
Figure~\ref{fig:hardall}. In this case, we may cache many resources
for months. Only a handful of resources had changed in the last
minutes. Since this is based on actual times since last modifications,
this suggests that many resources should have had explicit cache
headers with very long lifetimes. This is supported by
DyLDO\cite{dyldo2}, which concludes that:
\begin{quote}
[\ldots] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

@@

First, we compare dates given in \rdfterm{dct:modified} to dates given
in \httph{Last-Modified} when both are available for a resource. They
are often not the same, but it appears that dates in the former are
further back in time than the latter. We speculate that this may be
due to that the web-server tracks semantically insignificant changes
through the file system, while authors of RDF only update timestamp
when significant changes are made, or it may be that authors forget to
update their timestamps.

\rdfterm{dct:modified} occurs in 2687 triples, but 2487 of these does
not have the Request-URI of the information resource as their subject,
i.e. it gives the last modification time of some subgraph of the
returned RDF. Nevertheless, given its prevalence, it is highly likely
that the presence of \rdfterm{dct:modified} will be useful in
determining a heuristic freshness lifetime, as the latest date may be
used.

@@

Hitherto, we have considered the case where the client or proxy does
not send a HTTP request to the server when a resource that is present
in the cache is requested. This is desirable if the client can be
sufficiently confident that the response is fresh, either by having a
standards-compliant freshness lifetime or a heuristic to determine
it. At the end of this period, or if the previous response had no
lifetime, due to lack of information, or to that the server has stated
so in the \httph{Cache-Control} header, responses must be
revalidated. In this case, RFC7232 defines the behaviour, with
\httph{ETag} and \httph{Last-Modified} as the relevant response
headers.

@@

Estimating the freshness lifetime is a challenging problem for data
owners. It must necessarily involve the human users involved in the
publishing cycle since they are making a commitment about future
changes. Designing user support systems as well as interfaces that fit
the publisher's workflow is an important problem.

@@

Even though it is clear that other parts of the Web benefit greatly
from caching, and that the potential for HTTP metadata to better
reflect actual update practices in the Semantic Web is great,
estimating the actual impact of doing so should be done.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading. We also thank the anonymous
reviewers for extensive reviews.

%\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
%\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}
\input{paper1.bbl}

>>>>

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic.
RFC7232 \cite{rfc7232} defines conditional requests, and is also
important when constructing caches. As RFC7234 notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, caching is discussed throughout the Architecture of the
World Wide Web \cite{Jacobs:04:AWW}, and the definition of the
Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and could
provide great value to the Semantic Web.

@@

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. 
The objectives of this paper are:
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}
The contributions of this paper are to meet these objectives by means
of a survey that shows that while the uptake has been moderate,
practical benefits may be realized already. Based on this survey as
well as practical experience, we point out future research directions
as well as some recommendations for deployed implementations.

@@

Caching may be deployed at several different levels: An HTTP cache may
be in a reverse proxy close to the server, in which case it may have
much in common with a conventional database cache. It may also be
anywhere between a server and a client, in which case it may be
shared, i.e. it may cache responses from a number of servers to
many clients. Another example is an institutional forward proxy,
which are close to several users. Finally, the User Agent may
implement a private cache for its user at the client side.

@@

As mentioned, the two documents from the HTTP 1.1 standards suite that
are relevant for this study are RFC7234, named ``Caching'',
and RFC7232, named ``Conditional Requests''. The main difference is
that the caching standard defines when a response may be reused
without any contact to origin server, whereas the conditional
requests define how to validate a response by contacting the origin
server. The two can be combined: Clients and proxies may use the
latter to revalidate a response that has been cached based on the
former.

RFC7234 defines two important headers. The first of which is \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used. The second is \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In this article, \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. It can also
be based on heuristics, Section~4.2.2 in RFC7234 provides some loose
constraints for such practice as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
freshness lifetime beforehand. However, the server is then required to be able to answer if the
resource has changed less expensively than it would be to serve the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients that have obtained these values
may use them to validate an earlier response by using
\httph{If-None-Match} and/or \httph{If-Modified-Since} respectively in
a subsequent request. If the server finds the response has not changed
based on this, it will respond with a \httph{304} status code and no
body, otherwise it will return the full response. The other headers we
recorded are listed in Table~\ref{tab:headers}.

@@

We are not aware of any surveys of this type. Although the database
literature is rich with query cache literature, it is mostly relevant
to what would happen within the server or between the server and a
reverse proxy, which is opaque to the Internet, and therefore not of
our concern. For the same reason, caching that happens within the
SPARQL engine is not relevant.

@@

Linked Data Fragments is claimed in \cite{ldf1} to take advantage of
caching and contrasts this with the unavailability of SPARQL query
caches. They assert that this is an architectural problem. In
\cite{hogan2014paths}, the authors examine cacheable as one of the
desiderata for sustainable data access. They claim, without further
justification, that SPARQL isn't cacheable.

@@

In \cite{umbrich2012hybrid}, the term caching was used in a different
sense than we use it. They rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.

In the broader Web literature, \cite{ager2010revisiting} analysed the
value of caching based anonymized traces of actual Web usage at a
major Internet Service Provider. They found that while caching often
yields little benefit when content is user-generated, there is still 
some potential.

@@

\section{Methodology}
We want to find information resources on the Web, and examine HTTP
headers that may allow caching. To do this, we perform GET requests on
SPARQL endpoints, vocabularies, dataset descriptions and other
resources and record headers recommended by current standards, as well
as obsoleted and non-standard headers. Additionally, we examine the
triples in the returned information resources to see if there is
information that may be used to calculate heuristic freshness.

We made several approaches to ensure that we visited a large and
representative section of the open Semantic Web. We took SPARQL
Endpoints from the SPARQLES survey \cite{buil2013sparql}, vocabularies
from Linked Open Vocabularies (LOV) \cite{lov2} and prefix.cc, and we
augmented these data with spidered data from the Billion Triple
Challenge (BTC) 2014 \cite{btc-2014} dataset. Of these, BTC2014 is by
far the largest, the others are small, curated and targeted
datasets. However, the size is besides the point, we were only
interested in examining as many hosts as possible, and they are still
few.

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. This was seeded
from datahub.io (aka CKAN), as well as other sources. To compile a list of
candidates for further examination, we performed a series of data reduction
steps, manually inspecting the result between each step. The details
of this process are given in a companion technical report
\cite{kjernsmo_add_survey_2015}.

@@

Key challenges to the validity of the survey are biases that may be
introduced by the coverage and then the data reduction. The breadth of
the Semantic Web is derived mainly from the BTC2014 crawl. While
LODstats\footnote{\url{http://stats.lod2.eu/}} has presently seen an
order of magnitude more triples, the number of error-free datasets
were at the time of this writing 4442. We work under the assumption
that cache headers are set mostly on a per-host basis, and if this
assumption is valid, sampling a URL per host is sufficient. LODstats
do not report per-host statistics, but often one host will host
several datasets. Another recent crawl was reported by
\cite{stateoflod2014}. It is not clear how many hosts were crawled, but the
number of triples is much smaller than that of
BTC2014. It is therefore a fair assumption that BTC2014 fairly well
represents the breadth of the Semantic Web, momentarily at least.

@@

First, we investigated whether certain server implementations provided
better support for caching than others. To do this, we formulated
SPARQL queries to examine the \httph{Server} headers of successful
responses. We used optional clauses matching the standards-compliant
computed freshness lifetime (which is the ideal) as well as whether
the response had other indications of caching-related metadata that
may assist caching such as modification time, certain predicates, etc.

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable
metadata. For the former, this amounted to 22 servers, which are
listed in Table~\ref{tab:servers}.  70 servers always responded with
usable metadata. Inspecting the values we find the well-known Virtuoso
and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which are partly
developed by and run on a server operated by this author. Apart from
those, we see that the they reveal very little about the RDF-specific
parts of the underlying server implementation. A quick inspection of
all \httph{Server} headers confirmed that few reveal any further
detail.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in the companion technical report
\cite{kjernsmo_add_survey_2015}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints. DBPedia has historically been updated
only a few times a year, but this was probably chosen to avoid
making a commitment far into the future. It may provide considerable benefits.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. Firstly, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001 (note, however, it is more contrived
than above, since the bins are like in Figure~\ref{fig:hardtable},
which is chosen for intuitive interpretation rather than statistical
rigor). Secondly, we note that it is often prohibited to cache dataset
descriptions. This is odd, since statistics about datasets is usually
costly to compute and should be cached. The VoID specification
\cite{voidnote} also notes that the statistics are considered
estimates.

@@

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In
Figure~\ref{fig:heuristicall}, we see that the distribution of
lifetimes is radically different from the case in
Figure~\ref{fig:hardall}. In this case, we may cache many resources
for months. Only a handful of resources changed in the last
minutes. Since this is based on actual times since last modifications,
this suggests that many resources should have had explicit cache
headers with very long lifetimes. This is supported by
DyLDO\cite{dyldo2}, which concludes that:
\begin{quote}
[\ldots] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

@@

First, we compared dates given in \rdfterm{dct:modified} to dates given
in \httph{Last-Modified} when both are available for a resource. They
were often not the same, but it appeared that dates in the former are
further back in time than the latter. We speculated that this may be
due to that the web-server tracks semantically insignificant changes
through the file system, while authors of RDF only update timestamp
when significant changes are made, or it may be that authors forget to
update their timestamps.

\rdfterm{dct:modified} occured in 2687 triples, but 2487 of these does
not have the Request-URI of the information resource as their subject,
i.e. it gives the last modification time of some subgraph of the
returned RDF. Nevertheless, given its prevalence, it is highly likely
that the presence of \rdfterm{dct:modified} will be useful in
determining a heuristic freshness lifetime, as the latest date may be
used.

@@

So far, we have considered the case where the client or proxy does
not send a HTTP request to the server when a resource that is present
in the cache is requested. This is desirable if the client can be
sufficiently confident that the response is fresh, either by having a
standards-compliant freshness lifetime or a heuristic to determine
it. At the end of this period, or if the previous response have no
lifetime, due to lack of information, or to that the server has stated
so in the \httph{Cache-Control} header, responses must be
revalidated. In this case, RFC7232 defines the behaviour, with
\httph{ETag} and \httph{Last-Modified} as the relevant response
headers.

@@

Estimating the freshness lifetime is a challenging problem for data
owners. It must necessarily include the human users involved in the
publishing cycle since they are making a commitment about future
changes. Designing user support systems as well as interfaces that fit
the publisher's workflow is an important problem.

@@

Even though it is clear that other parts of the Web benefit greatly
from caching, and that the potential for HTTP metadata to better
reflect actual update practices in the Semantic Web is great,
estimating the actual impact of doing so should be a topic for further research.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, Axel Polleres for encouraging comments
and Jonas Smedegaard for proofreading. We also thank the anonymous
reviewers for extensive reviews. Many to Helen Murray for linguistic
assistance.

%\bibliographystyle{plain}
\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}
%\input{paper1.bbl}
